Ice sheet mass flows

### 2024-06-24 sankey.tex
Improve labels (all rotated the same)

    \newcommand\abovelabel[2]{ % valname, label
      \node[font=\tiny, rotate=45, anchor=north west]
      at ([yshift=5mm,xshift=-3mm]#1.center) {\qq{#1}: #2};
    }
    \newcommand\belowlabel[2]{ % valname, label
      \node[font=\tiny, rotate=-45, anchor=south west]
      at ([yshift=-6mm,xshift=-3mm]#1.center) {\qq{#1}: #2};
    }

@@

      \node[font=\tiny, anchor=north]
      at ([yshift=-2mm,xshift=3mm]SUaa.east) {\qq{SUa}: Sublimation};

      \node[font=\tiny, anchor=north]
      at ([yshift=-2mm,xshift=0mm]EVa.west) {\qq{EVa}: Evaporation};

      \node[font=\tiny, anchor=west, rotate=-90]
      at ([yshift=0.5mm,xshift=1mm]RFZi.center) {\qq{RFZi}: Refreezing};

>>>>

    \newcommand\abovelabel[2]{ % valname, label
      \node[font=\tiny, rotate=45, anchor=north west]
      at ([yshift=5mm,xshift=-3mm]#1.center) {\qq{#1}: #2};
    }
    \newcommand\belowlabel[2]{ % valname, label
      \node[font=\tiny, rotate=45, anchor=north east]
      at ([yshift=-2mm,xshift=0mm]#1.center) {#2: \qq{#1}};
    }

@@

      \node[font=\tiny, rotate=45, anchor=north east]
      at ([yshift=1mm,xshift=3mm]SUaa.south) {Sublimation: \qq{SUaa}};

      \node[font=\tiny, rotate=45, anchor=north east]
      at ([yshift=0mm,xshift=5mm]EVa.north) {Evaporation: \qq{EVa}};

      \node[font=\tiny, anchor=west, rotate=90]
      at ([yshift=-0.5mm,xshift=1mm]RFZo.center) {Refreezing: \qq{RFZi}};
